---
title: "A Template for `r2anki`-Flashcards"
output:
  html_document:
    theme: "flatly"
    # "readable"
    highlight: "pygments"
    # "kate"
    # "textmate"
    self_contained: false
---
```{r, echo = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE
)
```

# Atomics

## Strings

### Basic string operations

1. **Paste/concatenate strings.**
    
    ```{r, eval = TRUE}
    stringr::str_c("a", "b", NA, NaN, NULL, factor("lalala"), character(0))
    #   ____________________________________________________________________________
    paste("a", "b", NA, NaN, NULL, factor("lalala"), character(0), sep = "")
    ```

1. **Treat `NA`'s as strings (`"NA"`).**
    
    ```{r, eval = TRUE}
    stringr::str_replace_na(c(NA, NaN, factor("lalala"), character(0)))
    # note that the `c` function coerces the factor to its integer representation
    #   ____________________________________________________________________________
    base_replace_na <- function(x) {ifelse(is.na(x), "NA", x)}
    base_replace_na(c(NA, NaN, factor("lalala"), character(0)))
    ```

1. **Count the number of letters in a string.**

    ```{r, eval = TRUE}
    stringr::str_length(c("four", NA, NaN, NULL, factor("lalala")))
    #   ____________________________________________________________________________
    nchar(c("four", NA, NaN, NULL, factor("lalala")))
    ```

1. **Return the last letter of a string, subset a string.**

    ```{r, eval = TRUE}
    stringr::str_sub(c("five", "six"), -1)
    #   ____________________________________________________________________________
    substr(c("five", "six"), 
           start = nchar(c("five", "six")), 
           stop = nchar(c("five", "six")))
    ```
    
1. **Repeat/replicate/duplicate a string several times.**

    ```{r, eval = TRUE}
    stringr::str_dup("_a_", 5)
    #   ____________________________________________________________________________
    paste(rep("_a_", 5), collapse = "")
    ```
    
1. **Remove/trim spaces at the beginning (leading) and/or end (trailing) of a string.**

    ```{r, eval = TRUE}
    stringr::str_trim(c("  2left_1right ", "   "), side = c("left"))
    #   ____________________________________________________________________________
    # ^\\s+|\\s+$ is the regex for one or more spaces in the beginning
    # or one or more spaces at the end
    gsub("^\\s+", "", c("  2left_1right ", "   "))
    ```
    
1. **Fill/pad spaces (or other characters) before and/or after a string.**

    ```{r, eval = TRUE}
    stringr::str_pad(c("lalala", ""), width = 7)
    #   ____________________________________________________________________________
    unname(
      vapply(c("lalala", ""), 
             function(x) if(nchar(x) < 7) {
               paste0(rep(" ", 7 - nchar(x)), x, collapse = "")
               } else {x},
             character(1)
             )
      )
    ```
    
1. **Sort strings for example, by a different local alphabetic order.**

    ```{r, eval = TRUE}
    # The vowels come before the consonants in Hawaiian
    stringr::str_sort(letters[1:10], locale = "haw")
    #   ____________________________________________________________________________
    # one can use `sort()`, but one has to know the specific locale
    ```
    
1. **Return the order of stringelements within a specific alphabet**

    ```{r, eval = TRUE}
    # The vowels come before the consonants in Hawaiian
    stringr::str_order(letters[1:10], locale = "haw")
    #   ____________________________________________________________________________
    # one can use `sort()`, but one has to know the specific locale
    ```
    
1. **Change the encoding of a string**

    ```{r, eval = TRUE}
    # Example from encoding?stringi::stringi
    x <- rawToChar(as.raw(177))
    x
    stringr::str_conv(x, "ISO-8859-2") # Polish "a with ogonek", (run this line in RStudio)
    stringr::str_conv(x, "ISO-8859-1") # Plus-minus
    #   ____________________________________________________________________________
    ```
    
1. **Return the first two words of a string**

    ```{r, eval = TRUE}
    stringr::word("Hello, how are you?", 1, 2)
    #   ____________________________________________________________________________
    ```
    
1. **Format a string (change width, indentaion, ...).**

    ```{r, eval = TRUE}
    cat(stringr::str_wrap("Hello, how are you?", width = 10, indent = 0, exdent = 2))
    #   ____________________________________________________________________________
    ```

### Pattern matching

1. **Does a string contain a specific sequence of characters?**

    ```{r, eval = TRUE}
    stringr::str_detect(c("my number is 110", "call 911"), "\\d{3}")
    #   ____________________________________________________________________________
    grepl("\\d{3}", c("my number is 110", "call 911"))
    ```
   
1. **Return every string that contains a specific sequence of characters?**

    ```{r, eval = TRUE}
    stringr::str_subset(c("my number is 110", "call 911"), "\\d{3}")
    #   ____________________________________________________________________________
    grep("\\d{3}", c("my number is 110", "call 911"), value = TRUE)
    ```

1. **Return the (first) start and end index of substrings within a string?**

    ```{r, eval = TRUE}
    # use stringr::str_locate_all to get a matrix of all start and end indexes
    stringr::str_locate(c("my 112 number is 110", "call 911"), c("\\d{3}"))
    #   ____________________________________________________________________________
    # Use gregexpr to construct something similar to str_locate_all
    matches <- regexpr("\\d{3}", c("my 112 number is 110", "call 911"))
    
    # formatting
    match_lengths <- attr(matches, "match.length")
    attributes(matches) <- NULL
    match_indices <- matrix(c(matches, matches + match_lengths - 1), ncol = 2)
    colnames(match_indices) <- c("start", "end")
    
    # output
    match_indices
    ```

1. **Return the (first) matched substring within a string?**

    ```{r, eval = TRUE}
    # use stringr::str_extract_all to get a matrix of all matched substrings
    stringr::str_extract(c("my 112 number is 110", "call 911"), c("\\d{3}"))
    #   ____________________________________________________________________________
    # combine `substr()` with match_indices from above
    ```

1. **Return the matching strings and matched capture groups.**

    ```{r, eval = TRUE}
    # the example from the stringr vignette
    strings <- c(
      "apple",
      "219 733 8965", 
      "329-293-8753", 
      "Work: 579-499-7527; Home: 543.355.3679"
      )
    phone <- "([2-9][0-9]{2})[- .]([0-9]{3})[- .]([0-9]{4})"
    
    stringr::str_match(strings, phone)
    # Use stringr::str_match_all for list return
    #   ____________________________________________________________________________
    # `regmatches()`
    ```
    
1. **Replace/substitute the first matching subtstring within a string.**

    ```{r, eval = TRUE}
    stringr::str_replace(c("my 112 number is 110", "call 911"),
                         c("\\d{1}(\\d{2})"), "\\1\\1")
    #   ____________________________________________________________________________
    sub(c("\\d{1}(\\d{2})"), "\\1\\1", c("my 112 number is 110", "call 911"))
    ```
    
1. **Replace/substitute all matching subtstrings within a string.**

    ```{r, eval = TRUE}
    stringr::str_replace_all(c("my 112 number is 110", "call 911"),
                             c("\\d{1}(\\d{2})"), "\\1\\1")
    #   ____________________________________________________________________________
    gsub(c("\\d{1}(\\d{2})"), "\\1\\1", c("my 112 number is 110", "call 911"))
    ```    
    
1. **Split strings by any pattern into different (optionally n) pieces.**

    ```{r, eval = TRUE}
    # returns a matrix and padds with empty strings, when n is greater than the
    # number of pieces
    stringr::str_split_fixed(c("lalala lala la",
                               "blabla lala la"),
                             c(" ", "b"), 5)
    # returns a list
    stringr::str_split(c("lalala lala la",
                         "blabla lala la"),
                       c(" ", "b"), 5)
    #   ____________________________________________________________________________
    # returns a list, but does not have an n argument (however, it shouldn't be
    # too hard to create one).
    strsplit(c("lalala lala la",
               "blabla lala la"),
             c(" ", "b"))
    ```

1. **Set all characters to lower/upper case.**

    ```{r, eval = TRUE}
    stringr::str_to_lower("aBcDe")
    stringr::str_to_upper("aBcDe")
    #   ____________________________________________________________________________
    tolower("aBcDe")
    toupper("aBcDe")
    ```  

1. **Truncate a string.**

    ```{r, eval = TRUE}
    stringr::str_trunc("123456789", width = 7, side = "right", ellipsis = "")
    #   ____________________________________________________________________________
    ```  

#### Regular expressions

1. **Where can I learn about regular expressions?**

  *  `?stringr::modifiers` for special regular expression functionality of the stringr package.
  *  [reference sheet](http://www.regular-expressions.info/reference.html)
  *  [interactively test](http://regexr.com/)
  *  [Build a regular expressin](http://www.txt2re.com/)
  *  Try the `str_view()` function to see, which substring a regex matches
  
    ```{r, eval = TRUE}
    stringr::str_view(c("abc", "a.c_blabla", "bef"), "a\\.c")
    ```

1. **How to test regular expressions?**

  > When writing regular expressions, I strongly recommend generating a list of positive (pattern should match) and negative (pattern shouldn’t match) test cases to ensure that you are matching the correct components.
  
#### Modifiers

1.  **Count the number of words within a string.**

    ```{r, eval = TRUE}
    words <- c("These are some words. 
               Some more words.")
    stringr::str_count(words, stringr::boundary("word"))
    #   ____________________________________________________________________________
    sapply(gregexpr("\\W+", words), length) + 1
    length(unlist(strsplit(words, " ")))  # doesn't really work
    sapply(strsplit(words, " "), length)
    ```
    
1.  **Count the number of lines within a string.**

    ```{r, eval = TRUE}
    stringr::str_count(words, stringr::boundary("line_break")) -
    stringr::str_count(words, stringr::boundary("word"))
    #   ____________________________________________________________________________
    ```

1.  **Count the number of sentences within a string.**

    ```{r, eval = TRUE}
    stringr::str_count(words, stringr::boundary("sentence"))
    #   ____________________________________________________________________________
    ```

1.  **Split a string by characters.**

    ```{r, eval = TRUE}
    stringr::str_split(words, stringr::boundary("character"))
    #   ____________________________________________________________________________
    strsplit(words, "")
    ```

### List output

1. **How to work with string functions, that return lists?**

## Factors

**Task:** Reorder the levels of a factor by another variable.
```{r}
data(iris)

levels(iris$Species)

library(dplyr)
iris %>%
  group_by(Species) %>% 
  summarize(mean_Sepal_Length = mean(Sepal.Length)) %>% 
  arrange(desc(mean_Sepal_Length)) -> d

levels(iris$Species) <- d$Species
levels(iris$Species)
#   ____________________________________________________________________________


```


**Task:** Reverse the order of factor levels.
```{r}

#   ____________________________________________________________________________
levels(iris$Species) <- rev(levels(iris$Species))
```


**Task:** Change specific levels of a factor by name, while preserving the order.
```{r}

#   ____________________________________________________________________________
levels(iris$Species)[2] <- "Flower B"
```

**Task:** Move specific factor levels in front of all others.

```{r}
#   ____________________________________________________________________________
data(iris)
levels(iris$Species) <- c(levels(iris$Species)[2], levels(iris$Species)[-2])
```


**Task:** Join/bind/combine/compose/unite rare factor levels into one.
```{r}
mtcars$cyl %>% 
  factor() %>% 
  forcats::fct_lump(n = 1)  # better example needed

mtcars$cyl %>% 
  factor() %>%
  forcats::fct_collapse(Other = c("4", "6"))

#   ____________________________________________________________________________

```


**Task:** Join/bind/combine/compose/unite common factor levels into one.
```{r}

#   ____________________________________________________________________________


```


## Dates and times
**Task:** Convert a string into a date.
```{r}
lubridate::ymd("2017/02/20")
#   ____________________________________________________________________________
as.Date("2017/02/20")
as.Date(c("2017/02/20", "2017/02/21"))  # also works for vectors

format(Sys.Date(), "%a %b %d")

format(Sys.Date(), "%a, den %d %B %c")
# compare ?strptime

#strptime()

```

#### **Task**: Add days (as an integer) to a date.
```{r collapse = TRUE}
lubridate::ymd("2017/02/20") + 5
#   ____________________________________________________________________________
as.Date("2017/02/20") + 5
as.numeric(as.Date("2017/02/20"))
as.Date("2017/02/20") - as.numeric(as.Date("2017/02/20"))

as.Date(50, origin="2017-01-01")


dates <- c("02/27/92", "02/27/92", "01/14/92", "02/28/92", "02/01/92")
as.Date(dates, "%m/%d/%y") + 7
```

**Task:** Generate a (dense) sequence of days/years/months.
```{r}
lubridate::ymd("2015-01-01")+ months(0:23)

#   ____________________________________________________________________________
seq(as.Date("2015-01-01"), length=24, by="1 day")
seq(as.Date("2015-01-01"), length=24, by="1 month")
seq(as.Date("2015-01-01"), length=24, by="1 year")

# Alternative 1
zoo::as.yearmon("2010-01-01") + 0:2/12  # ist nicht wirklich base, ich weiß.
```


## Resources
* [stringr vignette](https://cran.r-project.org/web/packages/stringr/vignettes/stringr.html)
* [forcats 0.1 on RStudio blog](https://blog.rstudio.org/2016/08/31/forcats-0-1-0/)
* [lubridate vignette](https://cran.r-project.org/web/packages/lubridate/vignettes/lubridate.html)