---
title: "A Template for `r2anki`-Flashcards"
output:
  html_document:
    theme: "flatly"
    # "readable"
    highlight: "pygments"
    # "kate"
    # "textmate"
    self_contained: false
---
```{r, echo = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE
)
```

# Strings
<!-- Tags: strings-->
## Manipulating Strings
#### [strings01]: Concatenate Strings in base *R*
<!-- Tags: r2anki-demo, task-->
##### ------ FrontSide ------
How would you concatenate strings in `base` *R*?
(And how would the output differ from a `stringr`-solution?)

##### ------ BackSide ------
```{r, eval = TRUE}
paste("a", "b", NA, NaN, NULL, factor("lalala"), character(0), sep = "")
```
*Comment:* `stringr::str_c`-does handle `NA`s more strictly than `paste`.

# Dataprep
## Reading Data into R
#### [dataprep01] Saving to csv
##### ------ FrontSide ------
Write `df` to a csv. Rehearse the most important arguments.

##### ------ BackSide ------
```{r, echo = TRUE, eval = FALSE}
write.table(x, file = "", append = FALSE, quote = TRUE, sep = " ",
            eol = "\n", na = "NA", dec = ".", row.names = TRUE,
            col.names = TRUE, qmethod = c("escape", "double"),
            fileEncoding = "")
```


------------ General Template ------------

# Topic
<!-- Tags: *general tags for all cards in the topic* -->
## Subtopic
#### [id] Title for the Task
<!-- Tags: *additional tags for this specific card* -->
##### ------ FrontSide ------
Description of the task.

##### ------ BackSide ------
Solution for the task